### 2007-10-31 pkg/paper/Colorspace/article.Rnw
added another idea for an example/demo to the colorspace article
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@16 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
minor addition
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@17 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
minor additions
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@18 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

@@

HLS (and others) because you may have been given a colour in
such a (crappy) colorspace and want to convert it to something
better in order to work with it.

@@

>>>>

\textit{Why not use CIE XYZ for storage?  (especially because
sRGB has limited gamut)  Because CIE storage would
mean lots more conversions when sending output to graphics devices(?)}

@@

HSV and HLS (and others) because you may have been given a colour in
such a (crappy) colorspace and want to convert it to something
better in order to work with it.  And basically just for completeness!

@@

Another example is converting an entire image to greyscale
(as in the tiger example used in grImport talks).
